Self-reported LLM usage and results on a data science project: Evidence from a Canadian undergraduate data science course

### 2024-08-07 paper/paper.qmd
changed bin width

all_data |>
  select(mark) |>
  ggplot(aes(x = mark)) +
  geom_histogram(binwidth = 0.01) +
  labs(x = "Final paper mark (percentage)", y = "Count") +
  theme_minimal()

>>>>

all_data |>
  select(mark) |>
  ggplot(aes(x = mark)) +
  geom_histogram(binwidth = 0.05) +
  labs(x = "Final paper mark (percentage)", y = "Count") +
  theme_minimal()
